%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Positions of Responsibility}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Secretary} % Role
    {Programming Club, IIT Kanpur} % Title
    {IIT Kanpur} % Location
    {Apr 2019-present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for hosting institute-wide lectures on various programming topics, organize hackathons and offer projects.}
        \item {Contributor to open-source projects, used by campus community of approx 6,000 people.}
        \item {Responsible for spreading awareness and motivating students of the campus towards programming.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Company Coordinator} % Role
    {Students’ Placement Office, IIT Kanpur} % Title
    {IIT Kanpur} % Location
    {Aug. 2019-present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Coordinating with 100s of companies for the placement of about 1000 graduating students in the Placement drive 2019.}
        \item {Organising talks and sessions for internships and placement for pre-final year students.}
      \end{cvitems}
    }
    
    
   \cventry
    {Web Manager} % Role
    {Antaragni, IIT Kanpur} % Title
    {IIT Kanpur} % Location
    {Mar. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Responsible for developing and managing Antaragni’s website and mobile app.}
      \end{cvitems}
    }
    
    \cventry
    {Student Guide} % Role
    {Counselling Services IIT Kanpur} % Title
    {IIT Kanpur} % Location
    {Jul. 2019-present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Mentoring freshers for an overall academic and emotional support for generating inclusiveness.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
